Networked Character Devices

### 2011-12-12 report/paper.tex
Fixed paper.tex errors

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\label{sec:introduction}

}{\end{itemize}}

@@

When a device is being exported by NCD we would like it to give the
appearence of having essentially ``moved'' the device to the client 
by forbidding user level accesses on the server. This is not part 
of our current iteration of NCD, but it will be included as higher
level functionality is implemented. Aquiring a remote device will be
done through an advertisment protocol that exists in user space so
that details may be supplied about the server and how the connection
should be made (e.g. UDP vs TCP).  After this NCD's functionality on
the client exists in kernel space so as to maintain transparency to
user level operations. Once imported, a device should be accessed just
like a normal local device.  This is acheived by the NCD kernel module
intercepting accesses and sending them out over the network to the
server. On the server, a userspace daemon accesses the physical
device to emulate the client's activity. The overall structure of the
NCD system is present in figure 1.

@@

NFS was the first implementation of truly general information sharing
over remote network connections.  However, NFS uses a specific file
system and cannot interface directly with devices.\cite{nfs-source}

NBD (Network Block Device) was included into the Linux kernel starting
with version 2.1.101. It enables users to export block devices over the
network, allowing use of any filesystem. However, NBD provides no
exclusive access guarantees and users must ascertain on their own
whether the remote drive is being used.\cite{nbd-source}

CUSE (Character Device in User Space) is an extension of FUSE that
allows bringing a character device into a FUSE filesystem.  This allows
users to access the device directly and potentially export it using
user-level networking.\cite{cuse-article}

USB/IP is a project to share USB devices over IP. This project is
very similar to NCD (as USB devices are character devices) but is
tailored specifically to allow sharing USB devices over a
network connection by intercepting USB specific data and encapsulating
it in IP.\cite{usbip-source}

Plan 9 is a distributed operating system developed as a successor to
Unix by Bell Labs.  It implicitly allows sharing devices over a
network via file interfaces. However, plan 9 does not currently see
wide deployment.\cite{plan9-pike}

>>>>

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

@@

When a device is being exported by NCD we would like it to give the
appearence of having essentially ``moved'' the device to the client 
by forbidding user level accesses on the server. This is not part 
of our current iteration of NCD, but it will be included as higher
level functionality is implemented. Aquiring a remote device will be
done through an advertisment protocol that exists in user space so
that details may be supplied about the server and how the connection
should be made (e.g. UDP vs TCP).  After this NCD's functionality on
the client exists in kernel space so as to maintain transparency to
user level operations. Once imported, a device should be accessed just
like a normal local device.  This is acheived by the NCD kernel module
intercepting accesses and sending them out over the network to the
server. On the server, a userspace daemon accesses the physical
device to emulate the client's activity. The overall structure of the
NCD system is present in Figure \ref{fig:system-full}.

@@

NFS was the first implementation of truly general information sharing
over remote network connections.  However, NFS uses a specific file
system and cannot interface directly with devices \cite{nfs-source}.

NBD (Network Block Device) was included into the Linux kernel starting
with version 2.1.101. It enables users to export block devices over the
network, allowing use of any filesystem. However, NBD provides no
exclusive access guarantees and users must ascertain on their own
whether the remote drive is being used \cite{nbd-source}.

CUSE (Character Device in User Space) is an extension of FUSE that
allows bringing a character device into a FUSE filesystem.  This allows
users to access the device directly and potentially export it using
user-level networking \cite{cuse-article}.

USB/IP is a project to share USB devices over IP. This project is
very similar to NCD (as USB devices are character devices) but is
tailored specifically to allow sharing USB devices over a
network connection by intercepting USB specific data and encapsulating
it in IP \cite{usbip-source}.

Plan 9 is a distributed operating system developed as a successor to
Unix by Bell Labs.  It implicitly allows sharing devices over a
network via file interfaces. However, Plan 9 does not currently see
wide deployment \cite{plan9-pike}.
